Response to reviewers

### 2022-05-10 response/response2.Rmd

This is more of a comment than a request to make a change, but we agree that this is an area that could be a good classroom discussion. We have added a couple of additional sentences to highlight the richness of this topic, and alternative approaches that might be explored. XXX DC to do

>>>>

This is more of a comment than a request to make a change, but we agree that this is an area that could be a good classroom discussion. We have revised the section on handling extremes to make our explanation simpler, with links to the shiny app that we put together to assist in the judgement and choice of threshold. We hope that this provides fodder for discussion. It could definitely be worked into a teaching exercise. XXX DONE
